parental migration and adolescents educational performance

### 2022-06-03 data/Gu-thesis-script.Rmd
bring back unadjusted model

@@

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
'Any Parent Absent' = did_adj_unres_cog,
'Only Mother Absent' = did_adj_unres_cog_m_only,
'Mother Absent' = did_adj_unres_cog_m,
'Only Father Absent' = did_adj_unres_cog_f,
'Mother Absent' = did_adj_unres_cog_f_only,
'Both Parents Absent' = did_adj_unres_cog_both) 
table_adj_unres_cog <- models_adj_unres_cog %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_f,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
'Any Parent Absent' = did_adj_unres_chn,
'Only Mother Absent' = did_adj_unres_chn_m_only,
'Mother Absent' = did_adj_unres_chn_m,
'Only Father Absent' = did_adj_unres_chn_f,
'Mother Absent' = did_adj_unres_chn_f_only,
'Both Parents Absent' = did_adj_unres_chn_both) 
table_adj_unres_chn <- models_adj_unres_chn %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"), output = 'markdown')
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_mat <- list(
'Any Parent Absent' = did_adj_unres_mat,
'Only Mother Absent' = did_adj_unres_mat_m_only,
'Mother Absent' = did_adj_unres_mat_m,
'Only Father Absent' = did_adj_unres_mat_f,
'Mother Absent' = did_adj_unres_mat_f_only,
'Both Parents Absent' = did_adj_unres_mat_both) 
table_adj_unres_mat <- models_adj_unres_mat %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"), output = 'markdown')
```

@@

Results
```{r}
models_adj_unres_eng <- list(
'Any Parent Absent' = did_adj_unres_eng,
'Only Mother Absent' = did_adj_unres_eng_m_only,
'Mother Absent' = did_adj_unres_eng_m,
'Only Father Absent' = did_adj_unres_eng_f,
'Mother Absent' = did_adj_unres_eng_f_only,
'Both Parents Absent' = did_adj_unres_eng_both) 
table_adj_unres_eng <- models_adj_unres_eng %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"), output = 'markdown')
```

>>>>

```{r}
df <- d_cl %>% select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1chn_std, w1mat_std, w1eng_std,
  cog, chn_std, mat_std, eng_std,
  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
  par.edu.year, home.book, home.internet
)
```

t-test
```{r}
t.test(w2cog3pl ~ migr, data = d_cl)
t.test(w2chn ~ migr, data = d_cl)
t.test(w2mat ~ migr, data = d_cl)
t.test(w2eng ~ migr, data = d_cl)
```

@@

## DID unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
```

Results
```{r}
models_unres_cog <- list(
'Any Parent Absent' = did_unres_cog,
'Only Mother Absent' = did_unres_cog_m_only,
'Mother Absent' = did_unres_cog_m,
'Only Father Absent' = did_unres_cog_f_only,
'Father Absent' = did_unres_cog_f,
'Both Parents Absent' = did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"))
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
```

Results
```{r}
models_unres_chn <- list(
'Any Parent Absent' = did_unres_chn,
'Only Mother Absent' = did_unres_chn_m_only,
'Mother Absent' = did_unres_chn_m,
'Only Father Absent' = did_unres_chn_f_only,
'Father Absent' = did_unres_chn_f,
'Both Parents Absent' = did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"))
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
```

Results
```{r}
models_unres_mat <- list(
'Any Parent Absent' = did_unres_mat,
'Only Mother Absent' = did_unres_mat_m_only,
'Mother Absent' = did_unres_mat_m,
'Only Father Absent' = did_unres_mat_f_only,
'Father Absent' = did_unres_mat_f,
'Both Parents Absent' = did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"))
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
```

Results
```{r}
models_unres_eng <- list(
'Any Parent Absent' = did_unres_eng,
'Only Mother Absent' = did_unres_eng_m_only,
'Mother Absent' = did_unres_eng_m,
'Only Father Absent' = did_unres_eng_f_only,
'Father Absent' = did_unres_eng_f,
'Both Parents Absent' = did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"))
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
'Any Parent Absent' = did_adj_unres_cog,
'Only Mother Absent' = did_adj_unres_cog_m_only,
'Mother Absent' = did_adj_unres_cog_m,
'Only Father Absent' = did_adj_unres_cog_f,
'Mother Absent' = did_adj_unres_cog_f_only,
'Both Parents Absent' = did_adj_unres_cog_both) 
table_adj_unres_cog <- models_adj_unres_cog %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           fmt = 2,
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_f,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
'Any Parent Absent' = did_adj_unres_chn,
'Only Mother Absent' = did_adj_unres_chn_m_only,
'Mother Absent' = did_adj_unres_chn_m,
'Only Father Absent' = did_adj_unres_chn_f,
'Mother Absent' = did_adj_unres_chn_f_only,
'Both Parents Absent' = did_adj_unres_chn_both) 
table_adj_unres_chn <- models_adj_unres_chn %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           fmt = 2,
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"), output = 'markdown')
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_mat <- list(
'Any Parent Absent' = did_adj_unres_mat,
'Only Mother Absent' = did_adj_unres_mat_m_only,
'Mother Absent' = did_adj_unres_mat_m,
'Only Father Absent' = did_adj_unres_mat_f,
'Mother Absent' = did_adj_unres_mat_f_only,
'Both Parents Absent' = did_adj_unres_mat_both) 
table_adj_unres_mat <- models_adj_unres_mat %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           fmt = 2,
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"), output = 'markdown')
```

@@

Results
```{r}
models_adj_unres_eng <- list(
'Any Parent Absent' = did_adj_unres_eng,
'Only Mother Absent' = did_adj_unres_eng_m_only,
'Mother Absent' = did_adj_unres_eng_m,
'Only Father Absent' = did_adj_unres_eng_f,
'Mother Absent' = did_adj_unres_eng_f_only,
'Both Parents Absent' = did_adj_unres_eng_both) 
table_adj_unres_eng <- models_adj_unres_eng %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
           fmt = 2,
           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"), output = 'markdown')
```
